---
title: "Dodson_R_Package"
author: "Tom Dodson"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Installation

Load in common libraries used by this package.

```{r}
library(ggplot2)
library(tidyverse)
```

Now, we install my R package:

```{r}
devtools::install_github("ThomasDodson/R_package_Dodson")
library("MorphoMussel")
```


Let us download some data for our package test:

```{r}
#' download.file()
```


## Working Example

+ An example of each function and how it works
+ Say something about why this is a good thing to do
+ Say something about expected output

```{r}
#' result <- mult(4, 5)
```



When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
